---
title: "df_to_graphml"
author: "Quentin Bukold"
date: "2023-01-21"
output: html_document
---

# libraries
```{r}
library(tidyr)
library(dplyr)
library(igraph)
#library(ggplot2)
#library(stringr)
```

# get narrow df 
structure:
node <- c("A", "A", "A", "B", "B")
to_node <- c("B", "C", "F", "A", "C")
sample <- data.frame(Name, Age)

```{r}
load(file.path(cache_dir,"dat_tweets_short_t_mentions.RDA"))

##delete rows with could cause ERROR
sample <- sample[!grepl("NULL", sample$mentions_user_id),]
sample <- sample %>% drop_na(mentions_user_id)
colnames(sample)
```

# get df for extra infos
node <- c("A", "B", "C", "D", "E")
party <- c("SPD", "CDU", "CDU", "FDP", "CSU")
```{r}
load(file.path(cache_dir,"total_list_nds.RDA"))
```

#create graph from df
```{r}
#get edge-list and convert to matrix
edges <- sample[, c("user_id","mentions_user_id")]

##Adjazenzmatrix (set to directed)
g <- get.adjacency(graph.edgelist(as.matrix(edges), directed=TRUE))

#create graph
g_dir <- graph.adjacency(g, mode = "directed", weighted=T)
## remove loops
g_dir <- simplify(g_dir)

```

# set labels and degrees of vertices, attributes of vertices and edges
```{r}
ix <- match(V(g_dir)$name, (total_list$user_id)) #(g_dir name = user_id)
V(g_dir)$label <- as.character(total_list$twitter_handle[ix])
V(g_dir)$party <- total_list$party[ix]
V(g_dir)$degree <- degree(g_dir)

degree_statistic<-data.frame(V(g_dir)$label, V(g_dir)$degree)
save(degree_statistic, file= file.path(cache_dir, 'degree_statistics.RDA'))
```

# create second contracted graph (not a must)
## contract a graph to a specific attribute (in this example party of politicians)
```{r}
#party_id
ids <- data.frame(Partei = c("AfD","CDU", "CSU", "DIE LINKE","FDP", "Bündnis 90/Die Grünen","SPD"), ID = c(1:7))
ix <- match(V(g_dir)$party, (ids$Partei))
V(g_dir)$party_id <- ids$ID[ix]
g_dir <- delete.vertices(g_dir, V(g_dir)[is.na(party_id)])
V(g_dir)$party_id

degree_statistic_2<-data.frame(V(g_dir)$label, V(g_dir)$party) 
#contract
g2<-contract(g_dir, mapping=V(g_dir)$party_id, vertex.attr.comb=first)
# remove loops
g2 <- igraph::simplify(g2)
V(g2)$label<-V(g2)$party
```

#get graphml file ###############
```{r}
write.graph(g_dir, file= file.path(cache_dir, 'seed_accounts_mentions_new.graphml'), format = 'graphml')
write.graph(g2, file= file.path(cache_dir, 'seed_partys_mentions_new.graphml'), format = 'graphml')
```
Further processing e.g. with Gephi